### 2014-06-06 paper/body.tex
small change

Once one has general features from some layer of a base network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \todo{cites}. The process that is usually followed is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second task. When following this path, one can choose to backpropagate the errors from the new task into the base features to \emph{fine-tune} them to the new task, or they can be left frozen. In cases where the second dataset is smaller than the first, fine-tuning the base features may result in overfitting, so the features are often left frozen. On the other hand, if the second dataset is large enough, the base features can be fine-tuned to the new task. Of course, if the second dataset is very large, there would be no need to transfer because the base filters could just be learned from scratch. These two domains --- fine-tuned features or frozen features --- are distinct and are compared later.

>>>>

Once one has general features from some layer of a base network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \todo{cites}. The process that is usually followed is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second task. When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left frozen or ``locked'', meaning that they do not change during training on the new task. In cases where the second dataset is smaller than the first, fine-tuning the base features may result in overfitting, so the features are often left frozen. On the other hand, if the second dataset is large enough, the base features can be fine-tuned to the new task. Of course, if the second dataset is very large, there would be little need to transfer because the base filters could just be learned from scratch. These two domains --- fine-tuned features or frozen features --- are distinct and are compared later.
